Making Soup: Preparing and Validating Models of the Bacterial Cytoplasm for Molecular Simulation

### 2019-12-03 paper/rebuttal.txt

Dear Prof. Amaro,

we were happy to receive constructive comments on our manuscript. We
have edited the manuscript according to the comments, and answered all
the questions. Please find a detailed list of replies below.

I hope the manuscript is acceptable in the present form and await your
decision.

Best regards,

David van der Spoel,
Uppsala University
Sweden.

@@

- Funding Sources: Authors are required to report ALL funding sources
  and grant/award numbers relevant to this manuscript. Enter all
  sources of funding for ALL authors relevant to this manuscript in
  BOTH the Open Funder Registry tool in ACS Paragon Plus and in the
  manuscript to meet this requirement. See
  http://pubs.acs.org/page/4authors/funder_options.html for complete
  instructions.
ANSWER: Funding information was updated.

- ORCID: Authors submitting manuscript revisions are required to
  provide their own validated ORCID iDs before completing the
  submission, if an ORCID iD is not already associated with their ACS
  Paragon Plus user profiles. This iD may be provided during original
  manuscript submission or when submitting the manuscript
  revision. You can provide only your own ORCID iD, a unique
  researcher identifier. If your ORCID iD is not already validated and
  associated with your ACS Paragon Plus user profile, you may do so by
  following the ORCID-related links in the Email/Name section of your
  ACS Paragon Plus account. All authors are encouraged to register for
  and associate their own ORCID iDs with their ACS Paragon Plus
  profiles. The ORCID iD will be displayed in the published article
  for any author on a manuscript who has a validated ORCID iD
  associated with ACS Paragon Plus when the manuscript is
  accepted. Learn more at http://www.orcid.org.
ANSWER: We have added one ORCID.

- On resubmission you must submit the following:
a) A point-by-point response to the reviewers.
b) A clean, unmarked copy of the manuscript document file.
c) A marked copy of the revised manuscript in which all the changes are clearly tracked or highlighted. Upload this file as Supporting Information for Review.
d) A clean, unmarked Supporting Information for Publication file, without any highlighting or tracked changes.

- The reviewers indicate that the quality of the written English could
  be improved. Please consider using a native English speaker or an
  English-language editing service to assist with this. The ACS
  maintains a list of editing services:
  https://authoringservices.acs.org/.
ANSWER: We carefully went over the manuscript text and fixed errors.

Please contact the JCIM editorial office at eic@jcim.acs.org if you
have any specific questions regarding these guidelines.
ANSWER: We did not manage to make a cover image unfortunately.

@@

2) Figure 1A: Even though it is not of importance for the message
conveyed by this figure, this reviewer nonetheless wonders what the
difference between the red and green particles is in that figure. A
short note on it in the caption would be appreciated.

ANSWER: Red is water and green is biomolecules, this has been added to
the caption.

3) p. 13-15: It is mentioned that the RMSD of TufA, MetE and IcdA is
larger in the cytoplasm than in diluted solutions. Based on the RMSF
they also identified which part of these proteins become more
flexible. The authors later speculate that this is due to some
nonspecific interactions. Here, some more analysis is required. The
authors should demonstrate that these changes indeed arise from such
kind of interactions and not more specific interactions. And why are
only certain loops of each protein involved while all other loops seem
almost unaffected. And why does the RMSF of residues 450-460 of MetE
decrease?

ANSWER: As explained in the text, the region comprised by residues
40-62 of TufA is a conformational switch that is known to be flexible,
residues 450-460 of MetE are a flexible loop and residues 1-8 of IcdA
form a flexible coil. Thus, one can expect these regions to display
variable conformational dynamics under different conditions. We
removed the speculation about the unspecific interactions and the
discussion about the RMSF difference (please see the answer to the
next question for details about this).

@@

4) Figure 5: Why are the standard errors of the RMSF for CspC so much
larger than for the other systems. Please comment.

ANSWER: Thank you for pointing that out. There was a mistake in the
statistics of our RMSF calculations.  We corrected it and updated the
RMSF plots. The errors are much smaller now and the overall shift
towards higher RMSF values for the protein cytoplasm models is no
longer present. Accordingly, the following sentences were removed from
the text:

@@

ANSWER: All fixed, thanks for finding these.

Reviewer: 2

Comments: Bortot et al. studied protein crowded systems using
molecular simulations with explicit solvent. MD simulations of
macromolecules in crowded conditions help us to understand protein
behaviors in a living cell. Recently, several computational scientists
performed MD simulations of multiple proteins in crowded conditions
and examined the differences of protein structure and dynamics in
crowded condition compared with that in dilute solution. In spite of
the importance of the research field, the paper has three critical
issues. At first, they used only small number of proteins and
tRNA(Phe) in the simulation system, although they call the set up as
the E. coli cytoplasm. Since the proteins can cover only 50 % of the
fraction of E. coli cytoplasm, it is difficult to call the system as
the E. coli cytoplasm. It should be called as a crowded condition that
mimic 50% of volume fraction of the cytosol of E. coli.

ANSWER: Obviously our model is not complete, to reflect this we
changed the title of the paper to "Making Soup: Preparing and
Validating Models of the Bacterial Cytoplasm for Molecular
Simulation". In the abstract the following sentence is added "The
model consists of 8 different proteins representing about 50% of the
cytoplasmic proteins and one type of t-RNA molecule."
